Experiences with Planning for Natural Language Generation

### 2009-06-03 trunk/Papers/ci-spark/experiments.tex
adjusted colors; added references to planenrs

In the second set of experiments, we evaluate the performance of several
planners on problems arising in the GIVE domain. Besides the FF, Metric-FF, and
SGPLAN planners we used in the previous set of experiments, we expand our
testing to include FF(h$_a$), LAMA, and C$^3$ \todo{citations}. Each of these
additional planners competed in the deterministic ``sequential, satifying''
track of the 2008 International Planning Competition; all planners generally
performed well on the competition domains, with LAMA the overall winner of
the track.\footnote{See \texttt{http://ipc.informatik.uni-freiburg.de/} for
details of the 2008 IPC.}

>>>>

In the second set of experiments, we evaluate the performance of
several planners on problems arising in the GIVE domain. Besides the
FF, Metric-FF, and SGPLAN planners we used in the previous set of
experiments, we expand our testing to include FF($h_a$)
\citep{keyder08:_ff_h_plann_for_plann}, LAMA
\citep{richter08:_lama_plann}, and C$^3$
\citep{lipovetzky08:_c3}. Each of these additional planners competed
in the deterministic ``sequential, satifying'' track of the 2008
International Planning Competition; all planners generally performed
well on the competition domains, with LAMA the overall winner of the
track.\footnote{See \texttt{http://ipc.informatik.uni-freiburg.de/}
  for details of the 2008 IPC.}
